National Longitudinal Evidence for Growth in Subjective Well-being from Spiritual Beliefs

### 2020-11-30 Manuscript_Bayesian.tex
fixed table small edits

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Longitudinal Wellbeing from Spiritual Beliefs}
\keywords{Belief, God, Health, Longitudinal, Panel, Religion, Spirit, Spirituality, Well-being\newline\indent Word count: 5181 words in text body, 1191 words in reference section}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

@@

\begin{table}[ ht ] 
\centering 
\caption{}\label{}
\scalebox{0.6}{
\begin{tabular}{ l c c c c c c c c c }
\toprule
 &   \multicolumn{ 9 }{c}{ Wave }\\ 
  & 2010 & 2011 & 2012 & 2013 & 2014 & 2015 & 2016 & 2017 & 2018 \\ 
 & n = \emph{missing} & n = \emph{missing} & n = 8547 & n = 13472 & n = \emph{missing} & n = 11687 & n = 16048 & n = 14174 & n = 14883 \\ 
 \midrule
Age &   &   &   &   &   &   &   &   &  \\ 
NZdep &   &   &   &   &   &   &   &   &  \\ 
Education &   &   &   &   &   &   &   &   &  \\ 
Employed &   &   &   &   &   &   &   &   &  \\ 
\hspace{6pt}    0 &  (\%) &  (\%) & 2094 (24.5\%) & 2955 (21.9\%) &  (\%) & 2525 (21.6\%) & 3486 (21.7\%) & 3223 (22.7\%) & 3404 (22.9\%)\\ 
\hspace{6pt}    1 &  (\%) &  (\%) & 6453 (75.5\%) & 10517 (78.1\%) &  (\%) & 9162 (78.4\%) & 12562 (78.3\%) & 10951 (77.3\%) & 11479 (77.1\%)\\ 
Ethnic\_Categories &   &   &   &   &   &   &   &   &  \\ 
\hspace{6pt}    Euro &  (\%) &  (\%) & 6731 (78.8\%) & 11024 (81.8\%) &  (\%) & 9671 (82.8\%) & 13389 (83.4\%) & 11814 (83.3\%) & 12427 (83.5\%)\\ 
\hspace{6pt}    Maori &  (\%) &  (\%) & 1188 (13.9\%) & 1608 (11.9\%) &  (\%) & 1341 (11.5\%) & 1749 (10.9\%) & 1620 (11.4\%) & 1677 (11.3\%)\\ 
\hspace{6pt}    Pacific &  (\%) &  (\%) & 284 (3.3\%) & 339 (2.5\%) &  (\%) & 277 (2.4\%) & 331 (2.1\%) & 243 (1.7\%) & 261 (1.8\%)\\ 
\hspace{6pt}    Asian &  (\%) &  (\%) & 344 (4\%) & 501 (3.7\%) &  (\%) & 398 (3.4\%) & 579 (3.6\%) & 497 (3.5\%) & 518 (3.5\%)\\ 
Male &   &   &   &   &   &   &   &   &  \\ 
\hspace{6pt}    0 &  (\%) &  (\%) & 5302 (62\%) & 8457 (62.8\%) &  (\%) & 7325 (62.7\%) & 10148 (63.2\%) & 9011 (63.6\%) & 9433 (63.4\%)\\ 
\hspace{6pt}    1 &  (\%) &  (\%) & 3245 (38\%) & 5015 (37.2\%) &  (\%) & 4362 (37.3\%) & 5900 (36.8\%) & 5163 (36.4\%) & 5450 (36.6\%)\\ 
Has\_Partner &   &   &   &   &   &   &   &   &  \\ 
\hspace{6pt}    0 &  (\%) &  (\%) & 2408 (28.2\%) & 3546 (26.3\%) &  (\%) & 2815 (24.1\%) & 3773 (23.5\%) & 3330 (23.5\%) & 3556 (23.9\%)\\ 
\hspace{6pt}    1 &  (\%) &  (\%) & 6139 (71.8\%) & 9926 (73.7\%) &  (\%) & 8872 (75.9\%) & 12275 (76.5\%) & 10844 (76.5\%) & 11327 (76.1\%)\\ 
Political\_Conservativism &   &   &   &   &   &   &   &   &  \\ 
Urban &   &   &   &   &   &   &   &   &  \\ 
\hspace{6pt}    Not\_Urban &  (\%) &  (\%) & 2865 (33.5\%) & 4278 (31.8\%) &  (\%) & 3951 (33.8\%) & 5538 (34.5\%) & 2610 (18.4\%) & 2661 (17.9\%)\\ 
\hspace{6pt}    Urban &  (\%) &  (\%) & 5682 (66.5\%) & 9194 (68.2\%) &  (\%) & 7736 (66.2\%) & 10510 (65.5\%) & 11564 (81.6\%) & 12222 (82.1\%)\\ 
Beliefs &   &   &   &   &   &   &   &   &  \\ 
\hspace{6pt}    \_Skeptic\_ &  (\%) &  (\%) & 2048 (24\%) & 3286 (24.4\%) &  (\%) & 2951 (25.3\%) & 4116 (25.6\%) & 3916 (27.6\%) & 4120 (27.7\%)\\ 
\hspace{6pt}    \_SpiritExcludesGod\_ &  (\%) &  (\%) & 2295 (26.9\%) & 3735 (27.7\%) &  (\%) & 3169 (27.1\%) & 4501 (28\%) & 3918 (27.6\%) & 3970 (26.7\%)\\ 
\hspace{6pt}    GodAndSpirit &  (\%) &  (\%) & 3707 (43.4\%) & 5499 (40.8\%) &  (\%) & 5119 (43.8\%) & 6453 (40.2\%) & 5464 (38.5\%) & 6210 (41.7\%)\\ 
\hspace{6pt}    GodExcludesSpirit &  (\%) &  (\%) & 497 (5.8\%) & 952 (7.1\%) &  (\%) & 448 (3.8\%) & 978 (6.1\%) & 876 (6.2\%) & 583 (3.9\%)\\ 
LIFESAT &   &   &   &   &   &   &   &   &  \\ 
PWI &   &   &   &   &   &   &   &   &  \\ 
\bottomrule

\end{tabular}
}
\end{table}

@@

The analysis was performed using R version 4.0.2 (2020-06-22). The Platform was x86\_64-apple-darwin17.0 (64-bit) Running under: macOS Catalina 10.15.6
We are greatful to the contributors and mantainers of the following packages:
R (Version 4.0.2; R Core Team, 2020) and the R-packages \emph{Amelia} (Version 1.7.6; Honaker et al., 2011a), \emph{citr} (Version 0.3.2; Aust, 2019), \emph{dplyr} (Version 1.0.2; Wickham et al., 2020), \emph{equatiomatic} (Version 0.1.0.9000; Anderson \& Heiss, 2020), \emph{forcats} (Version 0.5.0; Wickham, 2020a), \emph{ggeffects} (Version 0.15.0; Lüdecke, 2018), \emph{gghighlight} (Version 0.3.0; Yutani, 2020), \emph{ggplot2} (Version 3.3.2; Wickham, 2016), \emph{ggsci} (Version 2.9; Xiao, 2018), \emph{lme4} (Version 1.1.23; Bates et al., 2015), \emph{Matrix} (Version 1.2.18; Bates \& Maechler, 2019), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{parameters} (Version 0.8.6.1; D. Lüdecke et al., 2020a), \emph{patchwork} (Version 1.0.1; Pedersen, 2020), \emph{prettycode} (Version 1.1.0; Csárdi, 2019), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{Rcpp} (Version 1.0.5.1; Eddelbuettel \& François, 2011; Eddelbuettel \& Balamuta, 2017), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{report} (Version 0.1.0; Makowski, Dominique, Lüdecke, \& Daniel, 2019), \emph{see} (Version 0.5.2.1; D. Lüdecke et al., 2020b), \emph{sjPlot} (Version 2.8.4; D. Lüdecke, 2020), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{styler} (Version 1.3.2; Müller \& Walthert, 2020), \emph{table1} (Version 1.2; Rich, 2020), \emph{texreg} (Version 1.37.5; Leifeld, 2013), \emph{tibble} (Version 3.0.4; Müller \& Wickham, 2020), \emph{tidyr} (Version 1.1.2; Wickham, 2020b), and \emph{tidyverse} (Version 1.3.0; Wickham, Averick, et al., 2019)"

@@

\begin{table}
\begin{center}
\scalebox{0.5}{
\begin{tabular}{l c c}
\toprule
 & PWI & Life Sat \\
\midrule
Intercept                           & $\mathbf{7.14}$   & $\mathbf{5.29}$   \\
                                    & $ [ 7.11;  7.18]$ & $ [ 5.26;  5.31]$ \\
yearsC                              & $\mathbf{0.02}$   & $\mathbf{0.01}$   \\
                                    & $ [ 0.01;  0.02]$ & $ [ 0.00;  0.01]$ \\
Beliefs\_SpiritExcludesGod\_        & $\mathbf{-0.06}$  & $0.01$            \\
                                    & $ [-0.09; -0.03]$ & $ [-0.01;  0.03]$ \\
BeliefsGodAndSpirit                 & $\mathbf{-0.06}$  & $\mathbf{0.03}$   \\
                                    & $ [-0.09; -0.03]$ & $ [ 0.01;  0.06]$ \\
BeliefsGodExcludesSpirit            & $-0.00$           & $\mathbf{0.06}$   \\
                                    & $ [-0.04;  0.04]$ & $ [ 0.03;  0.09]$ \\
Age\_in\_Decades\_C                 & $\mathbf{0.07}$   & $\mathbf{0.08}$   \\
                                    & $ [ 0.06;  0.09]$ & $ [ 0.07;  0.09]$ \\
Ethnic\_CategoriesMaori             & $\mathbf{-0.38}$  & $\mathbf{-0.11}$  \\
                                    & $ [-0.43; -0.33]$ & $ [-0.14; -0.08]$ \\
Ethnic\_CategoriesPacific           & $\mathbf{-0.38}$  & $\mathbf{-0.15}$  \\
                                    & $ [-0.48; -0.29]$ & $ [-0.22; -0.09]$ \\
Ethnic\_CategoriesAsian             & $\mathbf{-0.09}$  & $-0.05$           \\
                                    & $ [-0.18; -0.01]$ & $ [-0.11;  0.02]$ \\
Male1                               & $\mathbf{-0.06}$  & $\mathbf{-0.16}$  \\
                                    & $ [-0.10; -0.02]$ & $ [-0.19; -0.13]$ \\
yearsC:Beliefs\_SpiritExcludesGod\_ & $\mathbf{0.01}$   & $\mathbf{0.01}$   \\
                                    & $ [ 0.00;  0.02]$ & $ [ 0.00;  0.02]$ \\
yearsC:BeliefsGodAndSpirit          & $\mathbf{0.01}$   & $\mathbf{0.01}$   \\
                                    & $ [ 0.01;  0.02]$ & $ [ 0.00;  0.02]$ \\
yearsC:BeliefsGodExcludesSpirit     & $0.00$            & $-0.00$           \\
                                    & $ [-0.01;  0.02]$ & $ [-0.01;  0.01]$ \\
\midrule
SD: Idsd(Intercept)                 & $1.42$            & $0.98$            \\
SD: Idsd(yearsC)                    & $0.13$            & $0.10$            \\
SD: Idcor(Intercept,yearsC)         & $-0.03$           & $0.03$            \\
\bottomrule
\end{tabular}
}
\caption{}
\label{tab:REGRESS_LS}
\end{center}
\end{table}

@@

\begin{figure}
\includegraphics[width=\textwidth]{/Users/jbul176/The Virtues Project Dropbox/Joseph Bulbulia/000GIT_STUFF/nzavs_spiritbeliefWellbeing/coefBayesDag} \caption{Coefficient Graphs}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{/Users/jbul176/The Virtues Project Dropbox/Joseph Bulbulia/000GIT_STUFF/nzavs_spiritbeliefWellbeing/pwi_confounder_adjusted} \caption{Personal Well-being prediction graph}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{/Users/jbul176/The Virtues Project Dropbox/Joseph Bulbulia/000GIT_STUFF/nzavs_spiritbeliefWellbeing/ls_counfounder_adjusted} \caption{Life satisfaction prediction graph}\label{fig:unnamed-chunk-3}
\end{figure}

>>>>

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Longitudinal Wellbeing from Spiritual Beliefs}
\keywords{Belief, God, Health, Longitudinal, Panel, Religion, Spirit, Spirituality, Well-being\newline\indent Word count: 5161 words in text body, 1191 words in reference section}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

@@

\begin{table}[h]
\begin{center}
\scalebox{0.45}{
\begin{tabular}[t]{llllllllllllllllllll}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{2}{c}{2010 (N=3820)} & \multicolumn{2}{c}{2011 (N=6153)} & \multicolumn{2}{c}{2012 (N=10385)} & \multicolumn{2}{c}{2013 (N=15836)} & \multicolumn{2}{c}{2014 (N=15026)} & \multicolumn{2}{c}{2015 (N=13665)} & \multicolumn{2}{c}{2016 (N=18071)} & \multicolumn{2}{c}{2017 (N=15779)} & \multicolumn{2}{c}{2018 (N=16501)} \\
\cmidrule(l{3pt}r{3pt}){3-4} \cmidrule(l{3pt}r{3pt}){5-6} \cmidrule(l{3pt}r{3pt}){7-8} \cmidrule(l{3pt}r{3pt}){9-10} \cmidrule(l{3pt}r{3pt}){11-12} \cmidrule(l{3pt}r{3pt}){13-14} \cmidrule(l{3pt}r{3pt}){15-16} \cmidrule(l{3pt}r{3pt}){17-18} \cmidrule(l{3pt}r{3pt}){19-20}
  &    & Mean & Std. Dev. & Mean  & Std. Dev.  & Mean   & Std. Dev.   & Mean    & Std. Dev.    & Mean     & Std. Dev.     & Mean      & Std. Dev.      & Mean       & Std. Dev.       & Mean        & Std. Dev.        & Mean         & Std. Dev.        \\
\midrule
Age &  & 51.0 & 14.7 & 50.9 & 15.5 & 50.2 & 14.8 & 48.6 & 14.0 & 49.7 & 14.0 & 51.0 & 13.9 & 50.9 & 13.6 & 51.9 & 13.6 & 52.7 & 13.5\\
NZdep &  & 4.8 & 2.8 & 4.6 & 2.7 & 4.9 & 2.8 & 4.7 & 2.8 & 4.7 & 2.8 & 4.7 & 2.8 & 4.6 & 2.7 & 4.6 & 2.7 & 4.6 & 2.7\\
Education &  &  &  &  &  & 5.8 & 2.8 & 6.0 & 2.8 & 6.1 & 2.8 & 6.2 & 2.8 & 6.4 & 2.7 & 6.5 & 2.7 & 6.5 & 2.7\\
Political\_Conservativism &  & 3.9 & 1.3 & 3.7 & 1.4 & 3.6 & 1.3 & 3.6 & 1.3 & 3.6 & 1.3 & 3.6 & 1.3 & 3.6 & 1.4 & 3.6 & 1.4 & 3.6 & 1.4\\
LIFESAT &  & 5.2 & 1.2 & 5.1 & 1.2 & 5.1 & 1.2 & 5.2 & 1.2 & 5.2 & 1.2 & 5.2 & 1.2 & 5.2 & 1.2 & 5.3 & 1.2 & 5.3 & 1.2\\
PWI &  & 6.8 & 1.7 & 6.8 & 1.7 & 6.8 & 1.7 & 7.0 & 1.7 & 7.0 & 1.7 & 7.1 & 1.7 & 7.1 & 1.7 & 7.1 & 1.7 & 7.1 & 1.6\\
\midrule
 &  & N & \% & N & \% & N & \% & N & \% & N & \% & N & \% & N & \% & N & \% & N & \%\\
Employed & 0 & 793 & 0.7 & 1276 & 1.1 & 2666 & 2.3 & 3531 & 3.1 & 3262 & 2.8 & 2972 & 2.6 & 4035 & 3.5 & 3655 & 3.2 & 3746 & 3.3\\
 & 1 & 2977 & 2.6 & 4795 & 4.2 & 7566 & 6.6 & 11991 & 10.4 & 11626 & 10.1 & 10378 & 9.0 & 14016 & 12.2 & 12070 & 10.5 & 12250 & 10.6\\
Ethnic\_Categories & Euro & 2947 & 2.6 & 4375 & 3.8 & 7881 & 6.8 & 12270 & 10.6 & 12051 & 10.5 & 10959 & 9.5 & 14641 & 12.7 & 12906 & 11.2 & 13475 & 11.7\\
 & Maori & 556 & 0.5 & 638 & 0.6 & 1489 & 1.3 & 1897 & 1.6 & 1830 & 1.6 & 1608 & 1.4 & 1964 & 1.7 & 1826 & 1.6 & 1872 & 1.6\\
 & Pacific & 110 & 0.1 & 126 & 0.1 & 343 & 0.3 & 408 & 0.4 & 400 & 0.3 & 336 & 0.3 & 385 & 0.3 & 286 & 0.2 & 296 & 0.3\\
 & Asian & 124 & 0.1 & 190 & 0.2 & 409 & 0.4 & 579 & 0.5 & 572 & 0.5 & 473 & 0.4 & 664 & 0.6 & 574 & 0.5 & 579 & 0.5\\
Male & 0 & 2390 & 2.1 & 3862 & 3.4 & 6542 & 5.7 & 10033 & 8.7 & 9500 & 8.2 & 8548 & 7.4 & 11377 & 9.9 & 9949 & 8.6 & 10388 & 9.0\\
 & 1 & 1430 & 1.2 & 2291 & 2.0 & 3843 & 3.3 & 5803 & 5.0 & 5478 & 4.8 & 5072 & 4.4 & 6635 & 5.8 & 5776 & 5.0 & 6077 & 5.3\\
Has\_Partner & 0 & 1054 & 0.9 & 1806 & 1.6 & 2988 & 2.6 & 4237 & 3.7 & 3664 & 3.2 & 3407 & 3.0 & 4274 & 3.7 & 3775 & 3.3 & 3931 & 3.4\\
 & 1 & 2764 & 2.4 & 4325 & 3.8 & 7331 & 6.4 & 11493 & 10.0 & 11130 & 9.7 & 10176 & 8.8 & 13613 & 11.8 & 11964 & 10.4 & 12078 & 10.5\\
Urban & Not\_Urban & 1531 & 1.3 & 2010 & 1.7 & 3512 & 3.0 & 5116 & 4.4 & 4894 & 4.2 & 4541 & 3.9 & 6223 & 5.4 & 2873 & 2.5 & 2938 & 2.5\\
 & Urban & 2271 & 2.0 & 3695 & 3.2 & 6709 & 5.8 & 10602 & 9.2 & 9937 & 8.6 & 8815 & 7.6 & 11622 & 10.1 & 12687 & 11.0 & 13291 & 11.5\\
Beliefs & \_Skeptic\_ & 625 & 0.5 & 1312 & 1.1 & 2235 & 1.9 & 3639 & 3.2 & 0 & 0.0 & 3278 & 2.8 & 4420 & 3.8 & 4135 & 3.6 & 4514 & 3.9\\
 & \_SpiritExcludesGod\_ & 778 & 0.7 & 1508 & 1.3 & 2535 & 2.2 & 4206 & 3.6 & 0 & 0.0 & 3542 & 3.1 & 4808 & 4.2 & 4148 & 3.6 & 4309 & 3.7\\
 & GodAndSpirit & 1751 & 1.5 & 2560 & 2.2 & 4181 & 3.6 & 6201 & 5.4 & 0 & 0.0 & 5780 & 5.0 & 7002 & 6.1 & 5771 & 5.0 & 6782 & 5.9\\
 & GodExcludesSpirit & 228 & 0.2 & 274 & 0.2 & 593 & 0.5 & 1137 & 1.0 & 0 & 0.0 & 523 & 0.5 & 1094 & 0.9 & 950 & 0.8 & 666 & 0.6\\
\bottomrule
\end{tabular}
\caption{Sample statistics by year}
\end{center}
\end{table}

@@

The analysis was performed using R version 4.0.2 (2020-06-22). The Platform was x86\_64-apple-darwin17.0 (64-bit) Running under: macOS Catalina 10.15.6
We are greatful to the contributors and mantainers of the following packages:
R (Version 4.0.3; R Core Team, 2020) and the R-packages \emph{Amelia} (Version 1.7.6; Honaker et al., 2011a), \emph{citr} (Version 0.3.2; Aust, 2019), \emph{dplyr} (Version 1.0.2; Wickham et al., 2020), \emph{equatiomatic} (Version 0.1.0.9000; Anderson \& Heiss, 2020), \emph{forcats} (Version 0.5.0; Wickham, 2020a), \emph{ggeffects} (Version 1.0.0; Lüdecke, 2018), \emph{gghighlight} (Version 0.3.0; Yutani, 2020), \emph{ggplot2} (Version 3.3.2; Wickham, 2016), \emph{ggsci} (Version 2.9; Xiao, 2018), \emph{lme4} (Version 1.1.25; Bates et al., 2015), \emph{Matrix} (Version 1.2.18; Bates \& Maechler, 2019), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{parameters} (Version 0.9.0.1; D. Lüdecke et al., 2020a), \emph{patchwork} (Version 1.1.0; Pedersen, 2020), \emph{prettycode} (Csárdi, 2019), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{Rcpp} (Version 1.0.5; Eddelbuettel \& François, 2011; Eddelbuettel \& Balamuta, 2017), \emph{readr} (Version 1.4.0; Wickham, Hester, \& Francois, 2018), \emph{report} (Version 0.2.0; Makowski, Dominique, Lüdecke, \& Daniel, 2019), \emph{see} (Version 0.6.0.1; D. Lüdecke et al., 2020b), \emph{sjPlot} (Version 2.8.6; D. Lüdecke, 2020), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{styler} (Version 1.3.2; Müller \& Walthert, 2020), \emph{table1} (Version 1.2.1; Rich, 2020), \emph{texreg} (Version 1.37.5; Leifeld, 2013), \emph{tibble} (Version 3.0.4; Müller \& Wickham, 2020), \emph{tidyr} (Version 1.1.2; Wickham, 2020b), and \emph{tidyverse} (Version 1.3.0; Wickham, Averick, et al., 2019)

@@

\begin{table}
\begin{center}
\scalebox{0.6}{
\begin{tabular}{l c c}
\toprule
 & PWI & Life Sat \\
\midrule
Intercept                           & $\mathbf{7.14}$   & $\mathbf{5.29}$   \\
                                    & $ [ 7.11;  7.18]$ & $ [ 5.26;  5.31]$ \\
yearsC                              & $\mathbf{0.02}$   & $\mathbf{0.01}$   \\
                                    & $ [ 0.01;  0.02]$ & $ [ 0.00;  0.01]$ \\
Beliefs\_SpiritExcludesGod\_        & $\mathbf{-0.06}$  & $0.01$            \\
                                    & $ [-0.09; -0.03]$ & $ [-0.01;  0.03]$ \\
BeliefsGodAndSpirit                 & $\mathbf{-0.06}$  & $\mathbf{0.03}$   \\
                                    & $ [-0.09; -0.03]$ & $ [ 0.01;  0.06]$ \\
BeliefsGodExcludesSpirit            & $-0.00$           & $\mathbf{0.06}$   \\
                                    & $ [-0.04;  0.04]$ & $ [ 0.03;  0.09]$ \\
Age\_in\_Decades\_C                 & $\mathbf{0.07}$   & $\mathbf{0.08}$   \\
                                    & $ [ 0.06;  0.09]$ & $ [ 0.07;  0.09]$ \\
Ethnic\_CategoriesMaori             & $\mathbf{-0.38}$  & $\mathbf{-0.11}$  \\
                                    & $ [-0.43; -0.33]$ & $ [-0.14; -0.08]$ \\
Ethnic\_CategoriesPacific           & $\mathbf{-0.38}$  & $\mathbf{-0.15}$  \\
                                    & $ [-0.48; -0.29]$ & $ [-0.22; -0.09]$ \\
Ethnic\_CategoriesAsian             & $\mathbf{-0.09}$  & $-0.05$           \\
                                    & $ [-0.18; -0.01]$ & $ [-0.11;  0.02]$ \\
Male1                               & $\mathbf{-0.06}$  & $\mathbf{-0.16}$  \\
                                    & $ [-0.10; -0.02]$ & $ [-0.19; -0.13]$ \\
yearsC:Beliefs\_SpiritExcludesGod\_ & $\mathbf{0.01}$   & $\mathbf{0.01}$   \\
                                    & $ [ 0.00;  0.02]$ & $ [ 0.00;  0.02]$ \\
yearsC:BeliefsGodAndSpirit          & $\mathbf{0.01}$   & $\mathbf{0.01}$   \\
                                    & $ [ 0.01;  0.02]$ & $ [ 0.00;  0.02]$ \\
yearsC:BeliefsGodExcludesSpirit     & $0.00$            & $-0.00$           \\
                                    & $ [-0.01;  0.02]$ & $ [-0.01;  0.01]$ \\
\midrule
SD: Idsd(Intercept)                 & $1.42$            & $0.98$            \\
SD: Idsd(yearsC)                    & $0.13$            & $0.10$            \\
SD: Idcor(Intercept,yearsC)         & $-0.03$           & $0.03$            \\
\bottomrule
\end{tabular}
}
\caption{}
\label{tab:REGRESS_LS}
\end{center}
\end{table}

@@

\begin{figure}
\includegraphics[width=\textwidth]{/Users/jbul716/The Virtues Project Dropbox/Joseph Bulbulia/000GIT_STUFF/nzavs_spiritbeliefWellbeing/coefBayesDag} \caption{Coefficient Graphs}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{/Users/jbul716/The Virtues Project Dropbox/Joseph Bulbulia/000GIT_STUFF/nzavs_spiritbeliefWellbeing/pwi_confounder_adjusted} \caption{Personal Well-being prediction graph}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{/Users/jbul716/The Virtues Project Dropbox/Joseph Bulbulia/000GIT_STUFF/nzavs_spiritbeliefWellbeing/ls_counfounder_adjusted} \caption{Life satisfaction prediction graph}\label{fig:unnamed-chunk-3}
\end{figure}
